---
output:
  md_document:
      variant: markdown_github
author: Yuhao Lin
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# qualtdict

**License:** [MIT](https://opensource.org/licenses/MIT)

[Qualtrics](https://www.qualtrics.com/) is an online survey and data
collection software platform. The qualtdict package builds on the
[qualtRics](https://github.com/ropensci/qualtRics) R package which
implements the retrieval of survey data using the Qualtrics API and aims to
reduce the pre-processing steps needed in analyzing such surveys. The
current package makes more comprehensive use of the survey metadata and
generates a variable dictionary inlucding most of the information essential
for data processing and analysis. It also uses a modified version of the
RAKE algorithm as implemented in the package
[slowraker](https://github.com/cran/slowraker) to generate meaningful names
for all variables in the survey, as well as adding a comprehensive set of
metadata attributes that uniquely identifies each variable.

## Installation

This package is in early stage of development and can be installed with the
[remotes](https://cran.r-project.org/package=remotes) package (or
[devtools](https://cran.r-project.org/package=devtools)):

Note that the package currently depends on my own fork of the qualtRics
package (the pull requests of which I have submitted).


```{r eval=FALSE}
install.packages("devtools")
devtools::install_github("lyh970817/qualtRics", ref = "qualtdict")
devtools::install_github("lyh970817/qultdict")
```

Optionally, install my fork of the sjlabelled package. The sjlabelled
allows adding label attributes to vectors. My fork fixes the issue where
labels cannot be set for vectors with only NAs.


```{r eval=FALSE}
devtools::install_github("lyh970817/sjlabelled")
```

## A demo workflow

You need to first register your Qualtrics credentials with the function
`qualtrics_api_credentials` exported from the package [qualtRics](https://www.qualtrics.com/).


```{r, eval=FALSE}
library(qualtdict)

qualtrics_api_credentials(api_key = "<YOUR-QUALTRICS_API_KEY>",
                          base_url = "<YOUR-QUALTRICS_BASE_URL>",
                          install = TRUE)
```

You can then generate a variable dictionary.

```{r, eval=FALSE}
mydict <- dict_generate("SV_4YyAHbAxpdbzacl", var_name = "question_name")
```

You may wish to generate meaningful variable names (if you don't already
have them in the survey) in the dictionary. If doing so, preferably you
would also want to define a function that extracts block prefixes from block names.

```{r, eval=FALSE}
# Define a block prefix extraction function
block_pattern <- function(x) {
  substring(x, 1, 3)
}

mydict <- dict_generate("SV_4YyAHbAxpdbzacl",
  var_name = "easy_name",
  block_pattern = block_pattern,
  block_sep = "."
)
```

And download labelled survey data with the dictionary.

```{r, eval=FALSE}
survey_dat <- get_survey_data(mydict,
  unanswer_recode = -77,
  unanswer_recode_multi = 0
)
```

