---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# qualtdict

**License:** [MIT](https://opensource.org/licenses/MIT)

<!-- badges: start -->
[![Project Status: WIP – Initial development is in progress, but there has not yet been a stable, usable release suitable for the public.](https://www.repostatus.org/badges/latest/wip.svg)](https://www.repostatus.org/#wip)
[![check-standard](https://github.com/lyh970817/qualtdict/actions/workflows/check-standard.yaml/badge.svg)](https://github.com/lyh970817/qualtdict/actions/workflows/check-standard.yaml)
[![test-coverage](https://github.com/lyh970817/qualtdict/actions/workflows/test-coverage.yaml/badge.svg)](https://github.com/lyh970817/qualtdict/actions/workflows/test-coverage.yaml)
<!-- badges: end -->

[Qualtrics](https://www.qualtrics.com/) is an online survey and data
collection software platform. The qualtdict R package builds on the
[qualtRics](https://github.com/ropensci/qualtRics) R package which
implements the retrieval of survey data using the Qualtrics API and aims to
reduce the pre-processing steps needed in analyzing such surveys. The
current package makes more comprehensive use of the survey metadata and
generates a variable dictionary including most of the information essential
for data processing and analysis. It also uses a modified version of the
RAKE algorithm implemented in the package
[slowraker](https://github.com/cran/slowraker) to generate meaningful names
for all variables in the survey, as well as adding a comprehensive set of
metadata attributes that uniquely identifies each variable.

## Installation

This package can be installed with the
[remotes](https://cran.r-project.org/package=remotes) package.

```{r eval=FALSE}
install.packages("remotes")
remotes::install_github("lyh970817/qultdict")
```

## Example

You need to first register your Qualtrics credentials with the function
`qualtrics_api_credentials` exported from the package 
[qualtRics](https://www.qualtrics.com/).


```{r, eval=FALSE}
library(qualtdict)

qualtrics_api_credentials(
  api_key = "<YOUR-QUALTRICS_API_KEY>",
  base_url = "<YOUR-QUALTRICS_BASE_URL>",
  install = TRUE
)
```

You can then generate a variable dictionary.

```{r, eval=FALSE}
mydict <- dict_generate("SV_4YyAHbAxpdbzacl", var_name = "question_name")
```

You may wish to generate meaningful variable names (if you don't already
have them in the survey) in the dictionary. If doing so, preferably you
would also want to define a function that extracts block prefixes from 
block names.

```{r, eval=FALSE}
# Define a block prefix extraction function
block_pattern <- function(x) {
  substring(x, 1, 3)
}

mydict <- dict_generate("SV_4YyAHbAxpdbzacl",
  var_name = "easy_name",
  block_pattern = block_pattern,
  block_sep = "."
)
```

You might want to check for potential mistakes in the survey with
`dict_validate`.

```{r, eval=FALSE}
dict_validate(mydict)
```

And use the dictionary to download
[sjlabelled](https://github.com/strengejacke/sjlabelled) survey data.

```{r, eval=FALSE}
survey_dat <- get_survey_data(mydict,
  unanswer_recode = -77,
  unanswer_recode_multi = 0
)
```
