---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# qualtdict

**License:** [MIT](https://opensource.org/licenses/MIT)

<!-- badges: start -->
```{r badges, echo = FALSE, results = "asis"}
cat(
  paste0(
    "[![Project Status: Active - The project has reached a stable, ",
    "usable state and is being actively developed.]",
    "(https://www.repostatus.org/badges/latest/active.svg)]",
    "(https://www.repostatus.org/#active)\n"
  ),
  paste0(
    "[![check-standard]",
    "(https://github.com/lyh970817/qualtdict/actions/workflows/",
    "check-standard.yaml/badge.svg)]",
    "(https://github.com/lyh970817/qualtdict/actions/workflows/",
    "check-standard.yaml)\n"
  ),
  paste0(
    "[![test-coverage]",
    "(https://github.com/lyh970817/qualtdict/actions/workflows/",
    "test-coverage.yaml/badge.svg)]",
    "(https://github.com/lyh970817/qualtdict/actions/workflows/",
    "test-coverage.yaml)\n"
  ),
  paste0(
    "[![Codecov test coverage]",
    "(https://codecov.io/gh/lyh970817/qualtdict/branch/main/",
    "graph/badge.svg)]",
    "(https://app.codecov.io/gh/lyh970817/qualtdict?branch=main)\n"
  ),
  sep = ""
)
```
<!-- badges: end -->

[Qualtrics](https://www.qualtrics.com/) is an online survey and data
collection software platform. `qualtdict` is a metadata and labelled-export
companion to [qualtRics](https://github.com/ropensci/qualtRics) for
Qualtrics surveys.

`qualtRics` owns API access to Qualtrics. `qualtdict` owns the package
workflow that turns Qualtrics metadata and import-ID response exports into:

- a **Variable Dictionary** with `response_column_id`, `qid`,
  `question_name`, `variable_name`, and survey metadata needed for analysis;
- **Validation Findings** that make dictionary consistency issues visible; and
- **Labelled Survey Data** whose Export Variables are renamed to
  `variable_name` and labelled from the Variable Dictionary.

`qualtdict` is not a replacement downloader for `qualtRics`, a general survey
cleaning framework, or a stable Semantic Name generator.

## Installation

This package can be installed with the
[remotes](https://cran.r-project.org/package=remotes) package.

```{r eval=FALSE}
install.packages("remotes")
remotes::install_github("lyh970817/qualtdict")
```

## Credentials And Offline Work

Live calls to `dict_generate()` and `fetch_labelled_survey_data()` require
Qualtrics API credentials because they retrieve metadata and responses through
`qualtRics`.
Register credentials with `qualtRics::qualtrics_api_credentials()`, which
`qualtdict` also re-exports for convenience.


```{r, eval=FALSE}
library(qualtdict)

qualtRics::qualtrics_api_credentials(
  api_key = "<YOUR-QUALTRICS_API_KEY>",
  base_url = "<YOUR-QUALTRICS_BASE_URL>",
  install = TRUE
)
```

Package tests and documentation examples avoid private survey data. Validation,
dictionary schema checks, block splitting, and labelled-export mechanics can be
tested offline with synthetic dictionaries and synthetic metadata. Only live
Qualtrics metadata or response downloads require credentials.

## Variable Dictionary To Labelled Survey Data

Generate a Variable Dictionary from a survey ID. The dictionary keeps
`response_column_id` as the downloaded response-column key, `qid` as the bare
Qualtrics question identifier, `question_name` as the raw Qualtrics naming
reference, and `variable_name` as the final export-safe Dictionary Variable
Name.

```{r, eval=FALSE}
survey_id <- "SV_XXXXXXXXXXXXXXXX"

dict <- dict_generate(
  survey_id,
  variable_name = "question_name"
)
```

Use `dict_validate()` to return structured Validation Findings.

```{r, eval=FALSE}
validation <- dict_validate(dict)
validation$validation_findings
```

Then create Labelled Survey Data. `qualtdict` calls
`qualtRics::fetch_survey()` with the response-column settings needed to match
downloaded data back to `response_column_id`, then renames Export Variables to
`variable_name` and attaches labels from the Variable Dictionary.

```{r, eval=FALSE}
survey_dat <- fetch_labelled_survey_data(
  dict,
  extra_columns = c("externalDataReference", "startDate", "endDate"),
  exclude_findings = "none",
  unanswer_recode = -77,
  unanswer_recode_multi = 0
)
```

If Qualtrics Question Names are not suitable as analysis names, you can ask
`qualtdict` to generate Semantic Names. Semantic Names are readable
conveniences generated from survey text and metadata; they are not stable
guarantees across package versions or survey text changes. For long text,
Semantic Names select important words from ranked keywords and preserve those
selected words in the order they appear in the naming text.

```{r, eval=FALSE}
block_pattern <- function(block) {
  substring(block, 1, 3)
}

dict <- dict_generate(
  survey_id,
  variable_name = "semantic_name",
  block_pattern = block_pattern,
  block_sep = "."
)
```
