---
title: "Introduction to qualtdict"
output: rmarkdown::html_vignette
author: Yuhao Lin
vignette: >
  %\VignetteIndexEntry{Introduction to qualtdict}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

`qualtdict` is a metadata and labelled-export companion to
[qualtRics](https://github.com/ropensci/qualtRics) for
[Qualtrics](https://www.qualtrics.com/) surveys. `qualtRics` owns API access:
authentication, metadata retrieval, and response downloads from Qualtrics.
`qualtdict` owns the package workflow that turns that metadata and those
import-ID response exports into a Variable Dictionary, Validation Findings, and
Labelled Survey Data.

The authors and contributors for this R package are not affiliated with
Qualtrics, and Qualtrics does not offer support for this R package.

## Main Workflow

The core workflow is:

1. Use `dict_generate()` to build a Variable Dictionary.
2. Use `dict_validate()` to inspect Validation Findings.
3. Use `get_survey_data()` to create Labelled Survey Data.

A Variable Dictionary preserves several distinct identifiers:

- `response_column_id`: the downloaded response column used to match raw
  Qualtrics response data to dictionary rows.
- `qid`: the bare Qualtrics question identifier, such as `QID1`.
- `question_name`: the raw Qualtrics Question Name.
- `variable_name`: the final export-safe Dictionary Variable Name used in
  Labelled Survey Data.
- `semantic_name`: a generated naming reference, present only when requested.

This vignette avoids private survey data. The live workflow chunks use a
placeholder survey ID and are not evaluated. The small table below shows the
shape of a safe simulated Variable Dictionary.

```{r}
example_dict <- data.frame(
  response_column_id = c("QID1", "QID1_3_TEXT"),
  qid = c("QID1", "QID1"),
  question_name = c("Q1", "Q1"),
  variable_name = c("Q1", "Q1.1"),
  block = c("Main Block", "Main Block"),
  question = c("Choose one", "Choose one"),
  item = c(NA, NA),
  level = c("1", "3_TEXT"),
  label = c("Yes", "Other_TEXT"),
  type = c("MC", "MC"),
  selector = c("SAVR", "SAVR"),
  sub_selector = c("TX", "TX"),
  content_type = c(NA, NA)
)

example_dict
```

## Credentials

Live calls to `dict_generate()` and `get_survey_data()` require Qualtrics API
credentials because they call Qualtrics through `qualtRics`. Your institution
must support API access and it must be enabled for your account. The person who
manages your Qualtrics account can help you find your API token and base URL.

```{r, eval=FALSE}
library(qualtdict)

qualtRics::qualtrics_api_credentials(
  api_key = "<YOUR-QUALTRICS_API_KEY>",
  base_url = "<YOUR-QUALTRICS_BASE_URL>",
  install = TRUE
)
```

Validation, dictionary schema checks, block splitting, and labelled-export
mechanics can be tested offline with synthetic dictionaries or recorded,
scrubbed fixtures. Only live metadata and response downloads require
credentials.

## Variable Dictionary

Generate a Variable Dictionary from a Qualtrics survey ID:

```{r, eval=FALSE}
survey_id <- "SV_XXXXXXXXXXXXXXXX"

dict <- dict_generate(
  survey_id,
  variable_name = "question_name"
)
```

With `variable_name = "question_name"`, `variable_name` is derived from the raw
Qualtrics Question Name and repaired as needed so Labelled Survey Data columns
are export-safe and unique. The original `question_name` remains in the
Variable Dictionary as a reference.

If Qualtrics Question Names are not suitable as analysis names, request
Semantic Names:

```{r, eval=FALSE}
block_pattern <- function(block) {
  substring(block, 1, 3)
}

dict <- dict_generate(
  survey_id,
  variable_name = "semantic_name",
  block_pattern = block_pattern,
  block_sep = "."
)
```

Semantic Names are best-effort readable conveniences generated from survey
text, block information, and response metadata. They are not stable guarantees
across package versions or survey text changes. Use them when they improve
analysis ergonomics, but do not treat them as permanent identifiers.

You can also preprocess the text used only for Semantic Name generation:

```{r, eval=FALSE}
drop_intro_text <- function(dict) {
  dict$question <- sub("^Please answer: ", "", dict$question)
  dict
}

dict <- dict_generate(
  survey_id,
  variable_name = "semantic_name",
  semantic_name_preprocess = drop_intro_text
)
```

`semantic_name_preprocess` receives the full post-normalisation dictionary and
runs only on the Semantic Name path. Temporary helper columns created by the
function are not included in the returned Variable Dictionary.

## Findings

`dict_validate()` returns a stable validation object with two components:
`validation_findings` and `level_label_pairs`.

```{r, eval=FALSE}
validation <- dict_validate(dict)

validation$validation_findings
validation$level_label_pairs
```

Validation Findings cover consistency issues in the generated Variable
Dictionary, including repaired `variable_name` values, non-unique or unsafe
Dictionary Variable Names, and level-label coding findings.

## Labelled Survey Data

Create Labelled Survey Data from a Variable Dictionary:

```{r, eval=FALSE}
survey_dat <- get_survey_data(
  dict,
  extra_columns = c("externalDataReference", "startDate", "endDate"),
  exclude_findings = "none",
  unanswer_recode = -77,
  unanswer_recode_multi = 0
)
```

`get_survey_data()` calls `qualtRics::fetch_survey()` with the settings needed
for reliable matching to `response_column_id`: `import_id = TRUE`,
`label = FALSE`, `convert = FALSE`, and `breakout_sets = TRUE`. You may pass
filtering arguments such as `include_questions`, but not arguments that would
override the response-column naming, labelling, conversion, or breakout
contract owned by `qualtdict`.

By default, variables with Validation Findings remain in the Labelled Survey
Data. Use `exclude_findings` only when you explicitly want to drop those
variables after download.

```{r, eval=FALSE}
survey_dat_clean <- get_survey_data(
  dict,
  exclude_findings = "validation"
)
```

## Survey Block Views

`dict_generate()` returns one Variable Dictionary and `get_survey_data()`
returns one Labelled Survey Data object. Use explicit helpers when you want
block-specific views:

```{r, eval=FALSE}
dict_by_block <- dict_split_blocks(dict)
data_by_block <- survey_split_blocks(survey_dat)
```
