---
title: "Introduction to qualtdict"
output: rmarkdown::html_vignette
author: Yuhao Lin
vignette: >
  %\VignetteIndexEntry{Introduction to qualtdict}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

[Qualtrics](https://www.qualtrics.com/) is an online survey and data
collection software platform. The qualtdict R package builds on the
[qualtRics](https://github.com/ropensci/qualtRics) R package which
implements the retrieval of survey data using the Qualtrics API and aims to
reduce the preprocessing steps needed in analyzing such surveys. The
current package makes more comprehensive use of the survey metadata
(retrieved via functions in
[qualtRics](https://github.com/ropensci/qualtRics)) and generates a
variable dictionary including most of the information essential for data
processing and analysis. It also uses a modified version of the RAKE
algorithm by [Rose. et al.]
(https://media.wiley.com/product_data/excerpt/22/04707498/0470749822.pdf)
implemented in the package [slowraker](https://github.com/cran/slowraker)
to generate meaningful names for all variables in the survey, as well as
adding a comprehensive set of metadata attributes that uniquely identifies
each variable.

Note that your institution must support API access and that it must be
enabled for your account. Whoever manages your Qualtrics account can help
you with this. Please refer to the [Qualtrics
documentation](https://api.qualtrics.com/) to find your API token.

The authors and contributors for this R package are not affiliated with
Qualtrics and Qualtrics does not offer support for this R package.

## Usage

* `dict_generate` to generate a `qualtdict`, a variable dictionary
  dataframe that can be later used to download actual survey data, or
  exported into a table file for provide straightforward overview of the
  survey variables.

* `dict_validate` to check for potential mistakes in the dictionary.

* `get_survey_data` to retrieve
  [sjlabelled](https://github.com/strengejacke/sjlabelled) survey data,
  where each variable is labelled with question, recodes (levels) and
  recode labels.

## Registering Qualtrics credentials

You need to first register your Qualtrics credentials with the function
`qualtrics_api_credentials` exported from the package 
[qualtRics](https://www.qualtrics.com/). 


```{r, eval=FALSE}
library(qualtdict)

qualtrics_api_credentials(
  api_key = "<YOUR-QUALTRICS_API_KEY>",
  base_url = "<YOUR-QUALTRICS_BASE_URL>",
  install = TRUE
)
```

## Generating a dictionary

You can then generate a variable dictionary.

```{r, eval=FALSE}
mydict <- dict_generate("SV_4YyAHbAxpdbzacl", var_name = "question_name")
```

Question names for each variable as set on Qualtrics will be used as
variable names

You may wish to generate meaningful variable names (if you don't already
have them in the survey) in the dictionary. If doing so, preferably you
would also want to define a function that extracts block prefixes from 
block names.

```{r, eval=FALSE}
# Define a block prefix extraction function
block_pattern <- function(x) {
  # Use the first three characters of a block name
  substring(x, 1, 3)
}

mydict <- dict_generate("SV_4YyAHbAxpdbzacl",
  var_name = "easy_name",
  block_pattern = block_pattern,
  block_sep = "."
)
```

These "easy names" are generated through a modified version of the RAKE
algorithm implemented in the package
[slowraker](https://github.com/cran/slowraker). The RAKE algorithm was
originally proposed as a method to extract keywords from documents [Rose.
et al.](https://media.wiley.com/product_data/excerpt/22/04707498/0470749822.pdf). 
It works by first selecting a series of candidate keywords, where each
candidate keyword is a set of contiguous words that doesn’t contain a
phrase delimiter or a meaningless stop word. Each single word within a
keyword is then scored by degree/frequency, where degree equals the number
of times that the word co-occurs with another word in another keyword, and
frequency is the total number of times that the word occurs overall. Each
candidate keyword is then scored by summing the scores of its member words.

The key modification of the algorithm in this package is that while the
candidate keywords for each variable are extracted from text components in
the survey associated with that variable (e.g. the overarching question as
well as the sub-question it belongs to, and for questions allowing for
selecting multiple choices , the choice labels), word frequency is calculated
as the number of times a word appears in the entire survey.

## Dictioanry validation

After downloading the dictionary, You might want to check for potential
mistakes in the dictionary with `dict_validate`, which returns a list of qids
with potential mistakes and mistake codes (explained in the function
documentation of `dict_validate`, as well as a list of unique level-label
pairing (numerals v.s. text labels), so that you can check that across a
number of questions measured on supposedly the same scale, there isn't a
question with distinct levels or labels to the others.

```{r, eval=FALSE}
dict_validate(mydict)
```

## Downloading survey with dictionary

And use the dictionary to download
[sjlabelled](https://github.com/strengejacke/sjlabelled) survey data
labelled with the associated text components from the survey (e.g.
question, recode labels and replacement strings in loop and merge
questions).

Extra parameters from `fetch_survey` in [qualtRics](https://github.com/ropensci/qualtRics) 
can be specified (e.g. `unanswer_recode` and `unanswer_recode_multi`).

```{r, eval=FALSE}
survey_dat <- get_survey_data(mydict,
  unanswer_recode = -77,
  unanswer_recode_multi = 0
)
```
